Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-08-23 paper/paper.tex
clean up paper repo
Remove `*.blg` file, tiny tweaks to `paper.tex`
added re-analysis of Steuerman et al
Added subdirectory (`figures/IFN_stochastic/SteuermanReanalysis/`)
that re-analyses data of Steuerman et al on single-cell
RNA-seq of flu-infected mice.

Then added Figure supplement (currently Figure 1 - Figure supplement 4)
that includes a summary of this re-analysis.

%%% start IFNrare figure %%%
\begin{figure}
\centerline{
{\bf \Large A}\includegraphics[width=0.25\textwidth,valign=t]{figures/IFN_stochastic/RussellVenn/venn_diagram.pdf}
{\bf \Large B}
{\bf \Large C}
}
\caption{
Triggering of IFN production is rare in influenza-infected cells.
{\bf (A)} Number of influenza-infected, NS-deficient, and IFN+ cells in our prior single-cell study of influenza infection of A549 cells.
The Venn diagram shows data aggregated over all samples from \citet{russell2018extreme}.
{\bf (B)} Number of IFN+ cells in the single-cell analysis of influenza-infected mice by \citep{steuerman2018dissection}.
\jdbcomment{We could possibly add a \emph{small simple} schematic of reporter line here as panel {\bf (C)} and move the current {\bf (C)} to {\bf (D)}, and then have more details in \FIGSUPP[IFNrare]{reporter_cells}.}
Alternatively, we could just show everything in \FIGSUPP[IFNrare]{reporter_cells}.
{\bf (C)} An A549 fluorescent-reporter cell-line confirms that IFN expression is very rare in cells infected with our relatively pure viral stock.
\jdbcomment{This should be a simple figure, such as a plot that just shows the fraction IFN+ among flu infected cells for a few replicates.
If you have suitable data, you could show for low, medium, and high-inducing stock and indicate which we use.
Then put detailed flow data similar to what is in your writeup in \FIGSUPP[IFNrare]{flow}. For that flow data, I think contour plots are better than overplotting. Also, don't subsample but show all points, as that will give better statistics.}
}
\label{fig:IFNrare}

\figsupp[Creation and validation of A549 fluorescent-reporter cell lines for type I and type III IFN expression.]
{CAPTION}
{IMAGE}
\label{figsupp:reporter_cells}

\figsupp[Expression of type I and type III IFN are highly correlated in influenza-infected A549 cells.]
{CAPTION}
{IMAGE}
\label{figsupp:type_I_vs_III}

\figsupp[Full flow cytometry data for \FIG{IFNrare}C.]
{CAPTION}
{IMAGE}
\label{figsupp:flow}

@@

\centerline{\jdbcomment{FIGURE}}

\caption{
Schematic of experimental approach.
}

>>>>

%%% start IFNrare figure %%%
\begin{figure}
\centerline{
{\bf \Large A}\includegraphics[width=0.25\textwidth,valign=t]{figures/IFN_stochastic/RussellVenn/venn_diagram.pdf}
{\bf \Large B}
{\bf \Large C}
}
\caption{
Triggering of IFN production is rare in influenza-infected cells.
{\bf (A)} Number of influenza-infected, NS-deficient, and IFN+ cells in our prior single-cell study of influenza infection of A549 cells.
The Venn diagram shows data aggregated over all samples from \citet{russell2018extreme}.
{\bf (B)} An A549 fluorescent-reporter cell-line confirms that IFN expression is very rare in cells infected with our relatively pure viral stock.
\jdbcomment{This should be a simple figure, such as a plot that just shows the fraction IFN+ among flu infected cells for a few replicates.
If you have suitable data, you could show for low, medium, and high-inducing stock and indicate which we use.
Then put detailed flow data similar to what is in your writeup in \FIGSUPP[IFNrare]{flow}. For that flow data, I think contour plots are better than overplotting. Also, don't subsample but show all points, as that will give better statistics.
We could possibly add a \emph{small simple} schematic of reporter line here as panel {\bf (B)} and move the current {\bf (B)} to {\bf (C)}, and then have more details in \FIGSUPP[IFNrare]{reporter_cells}.
Alternatively, we could just show everything in \FIGSUPP[IFNrare]{reporter_cells}.}
}
\label{fig:IFNrare}

\figsupp[Creation and validation of A549 fluorescent-reporter cell lines for type I and type III IFN expression.]
{CAPTION}
{\jdbcomment{ADD FIGURE}}
\label{figsupp:reporter_cells}

\figsupp[Expression of type I and type III IFN are highly correlated in influenza-infected A549 cells.]
{CAPTION}
{\jdbcomment{ADD FIGURE}}
\label{figsupp:type_I_vs_III}

\figsupp[Full flow cytometry data for \FIG{IFNrare}B.]
{CAPTION}
{\jdbcomment{ADD FIGURE}}
\label{figsupp:flow}

\figsupp[Few cells express detectable IFN in the single-cell analysis influenza-infected mice by \citet{steuerman2018dissection}.]
{A re-analysis of the data from \citet{steuerman2018dissection}'s single-cell mRNA-sequencing of cells from influenza-infected mice shows that only 5 of 1220 virus-infected cells express \emph{detectable} type I or type III IFN transcripts \textit{in vivo}.
Specifically, we downloaded the data from \citet{steuerman2018dissection} and identified influenza-infected cells using calling criteria similar to those described in \citet{steuerman2018dissection}.
Here we show statistics for the cells from the influenza-infected wildtype C57BL/6J mice, which were collected at 48 hours (two replicates) or 72 hours (1 replicate)---we do not show cells from the control mice.
As shown in the left-most panel, the sequencing depth of \citet{steuerman2018dissection} was quite low, with only $\sim$1,500 mRNA counts per cell on average (this is 10 to 15-fold lower than the sequencing depth in \citet{russell2018extreme} and the current study, respectively).
An important caveat is that this low sequencing depth could lead to a simple failure to detect IFN transcripts in some cells.
Nonetheless, there is detectable expression of key interferon-stimulated gene (ISG) mRNAs in the majority of infected cells (the middle panel shows the total counts of IFIT1, ISG15, CCL5, and Mx1).
However, only 5 of 1220 cells express any detectable type I (IFN$\alpha$ and IFN$\beta$) or type III (IFN$\lambda$) mRNAs, and only at low levels.
The full code that performs the re-analysis shown in this figure is at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/IFN_stochastic/SteuermanReanalysis/}.
}
{\includegraphics[width=0.8\textwidth]{figures/IFN_stochastic/SteuermanReanalysis/plots/p_mRNA_counts.pdf}}
\label{figsupp:mice}

@@

\centerline{\jdbcomment{FIGURE 2 HERE}}

\caption{
{\bf (A)} Schematic of experimental approach.
{\bf (B)} Some summary stats on numbers of cells, etc.
}
